% chktex-file 1 chktex-file 8 chktex-file 9 chktex-file 12 chktex-file 13 chktex-file 15 chktex-file 17 chktex-file 18 chktex-file 26 chktex-file 31 chktex-file 36 chktex-file 44
\documentclass[10pt]{article}
\input{/Users/mr.hassium/Desktop/Github/Hello-World/hassium.tex}
\def\htitle{Elementary Differential Geometry}
\def\hauthor{Hassium}\let\hfauthor\hauthor
\begin{document}
\hsetup
\htoc
\hmain
\section{Calculus on Euclidean Space}
\begin{definition}
    The \hdef{Euclidean 3-space}, denoted ${\R}^{3}$, is the set of ordered triples of the form $p=({p}_{1},{p}_{2},{p}_{3})$, where ${p}_{i}\in\R$. An element of ${\R}^{3}$ is called a \hdef{point}.
\end{definition}
\par
Let $p=({p}_{1},{p}_{2},{p}_{3}),q=({q}_{1},{q}_{2},{q}_{3})\in{\R}^{3}$ and let $a\in\R$. Define the addition to be $p+q=({p}_{i}+{q}_{i})$ and define the scalar multiplication to be $ap=(a{p}_{i})$. The additive identity $0=(0,0,0)$ is called the \hdef{origin} of ${\R}^{3}$. It is trivial that ${\R}^{3}$ is a vector space over $\R$.
\begin{definition}
    Let $x$, $y$, and $z$ be real-valued functions on ${\R}^{3}$ such that for all $p=({p}_{1},{p}_{2},{p}_{3})\in{\R}^{3}$, $x(p)={p}_{1}$. $y(p)={p}_{2}$, and $z(p)={p}_{3}$. We call $x$, $y$, and $z$ the \hdef{natural coordinate functions} of ${\R}^{3}$.
\end{definition}
\par
Let $x$, $y$, and $z$ be the natural coordinate functions, rewrite $x={x}_{1}$, $y={x}_{2}$, and $z={x}_{3}$. Then we have $p=({p}_{i})=({x}_{i}(p))$.
\begin{definition}
    A real-valued function $f$ on ${\R}^{3}$ is \hdef{differetiable} if all partial derivatives exist and continuous.
\end{definition}
\begin{definition}
    A subset $O\sub{\R}^{3}$ is \hdef{open} if for all $p\in O$, there exists $\ve>0$ such that $\{x\in{\R}^{3}\mid\norm{x-p}<\ve\}\sub O$. 
\end{definition}
\par
Let $f:O\to\R$ be a function defined on an open set. The differetiability of $f$ at $p$ can be determined entirely from values of $f$ on $O$. This means that differetiation is a local operation. We will give a proof of this later.
\begin{definition}
    A \hdef{tangent vector} ${v}_{p}$ is an ordered pair ${v}_{p}=(v,p)$, where $v,p\in{\R}^{3}$. Here $v$ is called the \hdef{vector part} and $p$ is called its \hdef{point of application}. Two tangent vectors are said to be \hdef{parallel} if they have the same vector part and different points of application.
\end{definition}
\begin{definition}
    Let $p\in{\R}^{3}$. The \hdef{tangent space} at $p$, denoted ${T}_{p}({\R}^{3})$, is the set of all tangent vectors that have $p$ as point of application.
\end{definition}
\par
Fix a tangent space ${T}_{p}({\R}^{3})$ and let ${T}_{p}({\R}^{3})$ adapt the operations from ${\R}^{3}\times{\R}^{3}$. We have a natural linear map $f:{T}_{p}({\R}^{3})\to{\R}^{3}$ defined by ${v}_{p}\to v$ and it is trivially an isomorphism. 
\begin{definition}
    A \hdef{vector field} $V$ on ${\R}^{3}$ is a function $V:{\R}^{3}\to{\R}^{3}$ such that for all $p\in{\R}^{3}$, $V(p)\sub{T}_{p}({\R}^{3})$.
\end{definition}
\par
Let $V$ and $W$ be vector field. Let $f$ be a real-valued function. For all $p\in{\R}^{3}$, define $V+W$ by $(V+W)(p)=V(p)+W(p)$ and $(fV)(p)=f(p)V(p)$.
\begin{definition}
    Let ${U}_{1}$, ${U}_{2}$, and ${U}_{3}$ be vector fields on ${\R}^{3}$ such that ${U}_{1}(p)={(1,0,0)}_{p}$, ${U}_{2}(p)={(0,1,0)}_{p}$, and ${U}_{3}(p)={(0,0,1)}_{p}$ for all $p\in{\R}^{3}$. We call $({U}_{1},{U}_{2},{U}_{3})$ the \hdef{natural frame field} on ${\R}^{3}$.
\end{definition}
\begin{proposition}
    Let $V$ be a vector field on ${\R}^{3}$. There are three uniquely determined real-valued functions ${v}_{1}$, ${v}_{2}$, and ${v}_{3}$ on ${\R}^{3}$ such that $V={v}_{1}{U}_{1}+{v}_{2}{U}_{2}+{v}_{3}{U}_{3}$.
\end{proposition}
\begin{proof}
    For all $p\in{\R}^{3}$, $V(p)={({v}_{1}(p),{v}_{2}(p),{v}_{3}(p))}_{p}={v}_{1}(p){(1,0,0)}_{p}+{v}_{2}(p){(0,1,0)}_{p}+{v}_{3}(p){(0,0,1)}_{p}={v}_{1}(p){U}_{1}(p)+{v}_{2}(p){U}_{2}(p)+{v}_{3}{U}_{3}(p)$, hence $V=\sum{v}_{i}{U}_{i}$.
\end{proof}
\par
The functions ${v}_{1}$, ${v}_{2}$, and ${v}_{3}$ are called the \hdef{Euclidean coordinate functions} on $V$.
\begin{definition}
    A vecotr field $V$ is \hdef{differetiable} if its Euclidean coordinate functions are differetiable.
\end{definition}






\input{Ch2.tex}
\input{ExPf.tex}
\hindex
\end{document}